DNSKEY Management

### 2012-12-10 paper/paper.tex
Todos cleanup

%% TODO description about registrars is wrong. They do not host DNS entries.
These two entities can eventually be linked by the third one, the registrar: this is where registrants will obtain the actual registration service, namely, the linking between a domain name and an IP address. Figure~\ref{fig:3Rs} illustrates the relations among the three R's.

@@

%% TODO again: IP updates (except the Name Servers) don't go through 3R
The entities behind the three R's are the exact same whether DNSSEC is used or not, but DNSSEC modifies the relations among them: e.g., DNSKEY updates will now also require communication between the three R's, even if no practical information like IP addresses or billing data was actually updated.

@@

%% TODO phrase is a bit clumsy
Enabling DNSSEC for a zone not being a \emph{do once and forget} operation, but instead requiring additional coordination among the three R's, let us see what managerial consequences arise, depending on if we cross or stay within certain administrative boundaries.

@@

\subsection{Computing power}
DNSSEC does not only require a higher coordination among the three R's, it also increases the strain on the computing infrastructure of a registrar when the size and quantity of the  zones it manages grow: updates to a zone or key rollovers require cryptographic signing operations that are orders of magnitude more expensive than simply updating a DNS record. Even with improvements like incremental signing~\cite{signMetrics}, the computational requirements are significant and must be considered when a registrar wishes to enable DNSSEC.
%TODO find good ref on this.

>>>>

These two entities can eventually be linked by the third one, the registrar: this is where registrants will obtain the actual registration service, namely, the linking between a zone name and their authoritative DNS servers. Figure~\ref{fig:3Rs} illustrates the relations among the three R's.

@@

The entities behind the three R's are the exact same whether DNSSEC is used or not, but DNSSEC modifies the relations among them: e.g., DNSKEY updates will now also require communication between the three R's, even if no practical information like DNS server addresses or billing data was actually updated.

@@

Enabling DNSSEC for a zone not isn't a \emph{do once and forget} operation, but requires additional coordination among the three R's. Let us see what managerial consequences arise, depending on if we cross or stay within certain administrative boundaries.

@@

\subsection{Computing power}
DNSSEC does not only require a higher coordination among the three R's, it also increases the strain on the computing infrastructure of a registrar when the size and quantity of the  zones it manages grow: updates to a zone or key rollovers require cryptographic signing operations that are orders of magnitude more expensive than simply updating a DNS record. Even with improvements like incremental signing~\cite{signMetrics}, the computational requirements are significant and must be considered when a registrar wishes to enable DNSSEC.
